% ProjetAMS.tex
% Main document using the local class: projectau.cls
% (See projectau.cls for provenance details and modification history.)


% Class options are set in projectau.cls.
% You can still override common ones here, e.g.:
% \documentclass[preprint,linenumbers,hidekeys]{projectau}
\documentclass[showkeys, twoside]{projectau}

% You may use additional packages here


% Project metadata


 \renewcommand{\formation}{Bachelor of Computer Science}
 \renewcommand{\promotion}{Promotion 2024}
 \renewcommand{\project}{Komnot_Detection Project}
 \renewcommand{\projectname}{Komnot_Detection}
\renewcommand{\headerlogo}{AU_LOGO}





%%%%%%%%%%%%%  Document starts here

\begin{document}

\pagestyle{fancy}


%%%%% You can edit here the document informations


\title{Komnot\_Detection: A Security API Gateway for Link Verification}% 


% Student

\author{Student Name}
 \affiliation{Cambodia Academy of Digital Technology.}
 \email{student@example.com}

% Promoters

 \author{First Promoter}%
 \author{Second Promoter}%
\affiliation{Promoter affiliations}%



\author{Third Promoter}
\affiliation{Another promoter affiliation}



\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
The proliferation of phishing attacks and malicious URLs poses significant threats to internet users and organizations worldwide, with particular relevance to developing countries like Cambodia where digital literacy and cybersecurity awareness remain limited. This thesis presents Komnot\_Detection, a comprehensive security API gateway designed to automatically verify URLs and protect users from malicious web content, specifically tailored for Cambodian users who face unique phishing patterns and language-specific scams.

The system employs a hybrid approach combining traditional blacklist/whitelist verification methods with advanced machine learning techniques to achieve high-accuracy URL classification. The implementation utilizes Python and Flask to create a modular, scalable API gateway capable of real-time URL analysis. The system was trained on a diverse dataset of 459 URLs, comprising 229 legitimate URLs sourced from Alexa Top Sites and trusted domains, and 230 malicious URLs collected from PhishTank database and enhanced with AI-generated phishing patterns using Google Gemini.

Comprehensive testing demonstrated robust performance with average response times of 45ms and the ability to handle concurrent requests effectively. The machine learning model, based on Logistic Regression, achieved 91.8\% accuracy on test data, with precision of 90.5\%, recall of 92.1\%, and F1-score of 91.3\%. Unit testing achieved 75\% pass rate, validating core functionality including URL parsing, feature extraction, and service integration.

Key features include automated feature extraction from URLs (14 distinct features including URL length, HTTPS protocol, domain characteristics, suspicious keywords, and entropy analysis), comprehensive security implementations (API key protection, input validation, rate limiting), and extensive API endpoints for integration. The system successfully addresses critical security concerns including protection against XSS attacks, secure deployment practices, and scalable architecture supporting future enhancements.

Results from integration testing validate the system's reliability and performance, with API endpoints demonstrating 98.5\% success rate for URL verification requests. Comparative analysis shows competitive performance against commercial solutions while maintaining cost-effectiveness and transparency. The hybrid verification pipeline ensures fast processing for known domains while providing intelligent analysis for unknown URLs through machine learning classification.

This research contributes significantly to the field of cybersecurity by providing an open-source, customizable solution for URL verification that can be deployed across various scales from individual users to enterprise environments. The modular architecture supports future enhancements and community contributions, establishing a foundation for ongoing development in automated threat detection. The system's focus on Cambodian-specific phishing patterns addresses a critical gap in localized cybersecurity solutions, potentially reducing scam incidents and improving digital safety in developing regions.

The thesis demonstrates practical implementation of advanced cybersecurity concepts, including feature engineering for URL analysis, machine learning model deployment in production environments, and API gateway design for real-time threat detection. The comprehensive evaluation methodology, combining quantitative performance metrics with qualitative security assessments, provides a robust framework for assessing cybersecurity tool effectiveness.

Future work includes expanding the dataset to thousands of URLs, implementing real-time threat intelligence integration, developing browser extensions, and enhancing support for international domain formats. The open-source nature of the project encourages community contributions and collaborative improvement of cybersecurity defenses against evolving phishing threats.
\end{abstract}

\keywords{URL detection, cybersecurity, machine learning, API gateway}%Use showkeys class option if keyword

% display desired
\maketitle
\thispagestyle{fancy}

\tableofcontents



\section{Introduction}
\label{sec:introduction}

\input{introduction.tex}

\section{Literature Review}
\label{sec:literature}

[Literature review content to be provided later]

\section{Methodology}
\label{sec:methodology}

\input{methodology.tex}

\chapter{Results and Evaluation}
\label{sec:results}

\input{results.tex}

\chapter{Discussion}
\label{sec:discussion}

\input{discussion.tex}

\chapter{Conclusion}
\label{sec:conclusion}

\input{conclusion.tex}

\begin{acknowledgments}
  Acknowledgments to be added later.
\end{acknowledgments}

% \appendix

% \section{Appendixes}

% If you need to provide supplementary information that may be of interest.


\bibliography{bibliography}% Produces the bibliography via BibTeX from file bibliography.bib.

\end{document}
%
% ****** End of file apssamp.tex ******
